The Truth is Revealed: Identity of the Fish Fry "Teti" Fishery in Eastern Cuba

### 2020-11-25 analysis/paper/paper.Rmd
travis4

```{r mainMap, fig.cap="Sampling site at Yumuri river mouth, Eastern Cuba", cache = TRUE}

@@

```{r gettingAPI, cache = TRUE}

@@

```{r editingAPI, cache = TRUE}

@@

```{r alignment, cache = TRUE}
invisible({capture.output({                ### ALIGNING the sequences        # libraries "msa" and "Biostrings"

@@

### Replacing gaps at the begining and end with Ns
gapsFasta <- read.fasta(file = "/Users/sheila_ffish/Documents/rrcompendium/analysis/data/raw_data/Sicydium_COI_6-alignment.fasta", seqtype = "DNA", as.string = TRUE, forceDNAtolower = FALSE)
replacingGaps <- lapply(gapsFasta, function(x) gsub("-", "N", x))
write.fasta(replacingGaps,names(replacingGaps),"/Users/sheila_ffish/Documents/rrcompendium/analysis/data/raw_data/Sicydium_COI_7-gaps.fasta")

@@

getBestModel <- function(fastaRF){
  if (class(fastaRF)!= c("DNAbin")){
    stop("This function only takes files of class 'DNAbin'. Use package 'ape' to read the input file")
  }
  formatPhyDat <- as.phyDat(fastaRF)                #getting the class used by modelTest: phyDat or pml
  modelChoice <- modelTest(formatPhyDat, tree = NULL, model = c("JC", "K80", "HKY", "TrN", "SYM", "GTR"), multicore = TRUE, mc.cores = 4)
  modelChoiceSorted <- modelChoice[order(modelChoice$AICc),]
  return(modelChoiceSorted)
}

@@

fit = optim.pml(fitStart, rearrangement = "stochastic", optGamma=TRUE, optInv=FALSE, model="HKY")     # seeking a maximum likelihood solution
bs = bootstrap.pml(fit, bs=100, optNni=TRUE, multicore=TRUE, mc.cores = 4)

@@

```{r figure_2, fig.cap = paste("ML phylogenetic tree  (-lnL =", loglikelihood,") depicting the relationships among all available COI sequences of the genus Sicydium (n=197). Sequences highlited in green represent samples from Cuba (n=6). Numbers on branches represent boostrap values higher than 70.")}

@@

#Sicydium_ML_tree

>>>>

```{r mainMap, fig.cap="Sampling site at Yumuri river mouth, Eastern Cuba"}

@@

```{r gettingAPI}

@@

```{r editingAPI}

@@

```{r alignment}
invisible({capture.output({                ### ALIGNING the sequences        # libraries "msa" and "Biostrings"

@@

### Replacing gaps at the begining and end with Ns
gapsFasta <- read.fasta(file = "/Users/sheila_ffish/Documents/rrcompendium/analysis/data/raw_data/Sicydium_COI_6-alignment.fasta", seqtype = "DNA", as.string = TRUE, forceDNAtolower = FALSE)
replacingGaps <- lapply(gapsFasta, function(x) gsub("-", "N", x))
write.fasta(replacingGaps, names(replacingGaps), "/Users/sheila_ffish/Documents/rrcompendium/analysis/data/raw_data/Sicydium_COI_7-gaps.fasta")

@@

getBestModel <- function(fastaRF){
  if (class(fastaRF)!= c("DNAbin")){
    stop("This function only takes files of class 'DNAbin'. Use package 'ape' to read the input file")
  }
  formatPhyDat <- as.phyDat(fastaRF)                #getting the class used by modelTest: phyDat or pml
  modelChoice <- modelTest(formatPhyDat, tree = NULL, model = c("JC", "K80", "HKY", "TrN", "SYM", "GTR"), multicore = TRUE, mc.cores = 4)
  modelChoiceSorted <- as.data.frame(modelChoice[order(modelChoice$AICc),])
  return(modelChoiceSorted)
}

@@

fit = optim.pml(fitStart, rearrangement = "stochastic", optGamma=TRUE, optInv=FALSE, model="HKY")     # seeking a maximum likelihood solution
#set.seed(123)    # getting the same tree topology each time the code runs 
bs = bootstrap.pml(fit, bs=100, optNni=TRUE, multicore=TRUE, mc.cores = 4)

@@

```{r Sicydium_ML_tree, fig.cap = paste("ML phylogenetic tree  (-lnL =", loglikelihood,") depicting the relationships among all available COI sequences of the genus Sicydium (n=197). Sequences highlited in green represent samples from Cuba (n=6). Numbers on branches represent boostrap values higher than 70.", fig.width = 11.8, fig.height = 9.84)}

@@

#Sicydium_ML_tree
```
